### 2014-03-17 src/analysis.Rnw
latest

#ggplot(df, aes(mutant.reduction, sd.reduction)) +
#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(shape=sampling, color=type)) + myopts
   geom_point(aes(shape=sampling, color=type),
   #position=position_jitter(width=0.1, height=0.1),
   size=3) +
   myopts +
   scale_color_manual(values = c('orange', 'purple', 'brown', 'red','blue', 'black'))
   # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
   #theme(legend.position=c(0,1) ,legend.justification=c(0,1))
@
\caption{The mean reduction of mutants vs its standard deviation. Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here. Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction}
%\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here. }
\label{fig:fullimgsize}
\end{figure*}

>>>>

#ggplot(df, aes(mutant.reduction, sd.reduction)) +
#   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(size=sqr, color=type)) + myopts
ggplot(df, aes(mutant.reduction, sd.reduction)) +
   labs(x=expression(mu[red]), y=expression(sigma[red]) ) +
#   geom_point(aes(shape=sampling, color=type)) + myopts
   geom_point(aes(shape=sampling, color=type),
   #position=position_jitter(width=0.1, height=0.1),
   size=3) +
   myopts +
   scale_color_manual(values = c('orange', 'blue', 'green', 'red','purple', 'black'))
   # block scale_color_manual(values = c('brown','orange', 'purple', 'green', 'red','blue', 'black'))
   #theme(legend.position=c(0,1) ,legend.justification=c(0,1))
@
\caption{The mean reduction of mutants vs its standard deviation. Original set, main variations of sampling, only observations with $R^2 > 0.9$ and $2\times \sigma_{red} < \mu_{red}$ are shown here. Notice that operator selection is has high $\sigma$ for corresponding $\mu$, and project based sampling is better for high reduction (note that x and y axis are in different scales)}
%\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times \sigma_{red} > \mu_{red}$ is shown here. }
\label{fig:fullimgsize}
\end{figure*}

### 2014-03-17 src/methodology.Rnw
latest

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion:} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

>>>>

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However, as seen in Figure~\ref{fig:op},
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.
